### 2022-02-16 README.Rmd
Test for github
Start to edit

Our pre-print is online here:

> Authors, (YYYY). _`r Title`_. Name of journal/book, Accessed `r format(Sys.Date(), "%d %b %Y")`. Online at <https://doi.org/xxx/xxx>

@@

The **analysis** directory contains:

  - [:file\_folder: paper](/analysis/paper): R Markdown source document
    for manuscript. Includes code to reproduce the figures and tables
    generated by the analysis. It also has a rendered version,
    `paper.docx`, suitable for reading (the code is replaced by figures
    and tables in this file)
  - [:file\_folder: data](/analysis/data): Data used in the analysis.
  - [:file\_folder: figures](/analysis/figures): Plots and other
    illustrations
  - [:file\_folder:
    supplementary-materials](/analysis/supplementary-materials):
    Supplementary materials including notes and other documents
    prepared and collected during the analysis.

>>>>

@@

The [:file: make.R](/make.R) allow to run the entire workflow used to produce the manuscript. However, fitting models on simulated data could several days to run. The **analysis** directory contains scripts that have been used to conduct the simulation (scripts starting with 'simu') and application (scripts starting with 'appli') analysis presented in the manuscript. Scripts have to be run following the order mentioned in their names.
